Analyzing Crime Trends in Toronto: Insights from the Police Annual Statistical Report

### 2024-09-27 paper/paper.qmd
Update: 1. Add "The remainder of this paper" in Introduction section.

# Data
The data used in this analysis was obtained from the Open Data Toronto portal [@OpenDataDataset]. The data set includes reported incidents categorized by type, division, and year, covering the period from 2014 to 2023.

@@

# Results
## Crime Distribution by Year
The dataset reveals fluctuating crime rates between 2014 and 2023. Property crimes such as auto theft have shown consistent increases, while personal crimes, such as sexual violations, remain relatively stable.

@@

# Discussion
The results of this analysis show clear trends in crime patterns across Toronto. Downtown areas  are significantly affected by property crimes like auto theft and break-ins, driven by dense population and high economic activity. Suburban areas, however, report more violent crimes, which may be influenced by socio-economic factors such as income inequality and access to social services [@Mohammadi_Bergquist].

@@

# Conclusion
This paper analyzed crime trends in Toronto using the Police Annual Statistical Report from 2014 to 2023. The findings demonstrate significant varieties in crime distribution across Toronto’s police divisions, with property crimes being more concentrated in downtown areas and violent crimes more prevalent in suburban regions. These insights are critical for shaping future crime prevention policies and ensuring the effective allocation of related resources.

>>>>

The remainder of this paper is structured as follows: @sec-data presents the data and the steps taken to clean and transform it for analysis. @sec-result discusses the results of the study, focusing on crime distribution trends by year, types of crimes by division, and clearance rates for different crime types. @sec-discussion interprets the findings in the broader context of urban crime trends and offers insights for future research. Finally, @sec-conclusion concludes the paper by summarizing key takeaways and recommending strategies for crime prevention and law enforcement improvement in Toronto.

# Data {#sec-data}
The data used in this analysis was obtained from the Open Data Toronto portal [@OpenDataDataset]. The data set includes reported incidents categorized by type, division, and year, covering the period from 2014 to 2023.

@@

# Results {#sec-result}
## Crime Distribution by Year
The dataset reveals fluctuating crime rates between 2014 and 2023. Property crimes such as auto theft have shown consistent increases, while personal crimes, such as sexual violations, remain relatively stable.

@@

# Discussion {#sec-discussion}
The results of this analysis show clear trends in crime patterns across Toronto. Downtown areas  are significantly affected by property crimes like auto theft and break-ins, driven by dense population and high economic activity. Suburban areas, however, report more violent crimes, which may be influenced by socio-economic factors such as income inequality and access to social services [@Mohammadi_Bergquist].

@@

# Conclusion {#sec-conclusion}
This paper analyzed crime trends in Toronto using the Police Annual Statistical Report from 2014 to 2023. The findings demonstrate significant varieties in crime distribution across Toronto’s police divisions, with property crimes being more concentrated in downtown areas and violent crimes more prevalent in suburban regions. These insights are critical for shaping future crime prevention policies and ensuring the effective allocation of related resources.
